JLyrics \titlenote{Submitted as the final project for CS 410 Summer 2014.}

### 2014-08-01 report/paper.tex
Added images. Finished mojibake section.

\documentclass{acm} % this finds the file "acm.bst"
\usepackage[utf8]{inputenc}
\usepackage{CJK,CJKspace,CJKpunct}
\usepackage{cite,graphicx}

@@

@@

Secondly, finding information on the song itself can assist the listener in learning foreign languages. Repetition is the best methods for learning. Listening to enjoyable music and recognizing new words each time the song is played is a fun way to strengthen one's language capabilities through repetition. Many music players such as foobar2000 and Rocket Player will display the lyrics of a song that is being played so long as those lyrics have been embedded into the music file as a tag. This feature can be used in tandem with the learner's interest in following along with the song to promote learning the language. If one is clever, they could put the same lyrics into the karaoke variant of the song and practice singing to improve their reading and speaking abilities. Regardless of the reason, they user would need to find the full lyrics from the song. We want to help with this cause.

TODO: Picture of Rocket Player or foobar2000

@@

Despite all efforts to keep our encodings straight, nothing could get Windows' command prompt, cmd, to behave as we would have wanted it to.

TODO: Add pictures of command prompts

@@

>>>>

\documentclass{acm} % this finds the file "acm.bst"
\usepackage{easyfig}
\usepackage[utf8]{inputenc}
\usepackage{CJK,CJKspace,CJKpunct}
\usepackage{cite,graphicx}

@@

\easyfigdefault{placement={!htb}, max width=20pc, max height=\textheight, keepaspectratio}

@@

Secondly, finding information on the song itself can assist the listener in learning foreign languages. Repetition is the best methods for learning. Listening to enjoyable music and recognizing new words each time the song is played is a fun way to strengthen one's language capabilities through repetition. Many music players such as foobar2000 and Rocket Player will display the lyrics of a song that is being played so long as those lyrics have been embedded into the music file as a tag. An example screenshot of Rocket Player showing a song's lyrics is in Figure~\ref{fig:res/rocket-player.png} This feature can be used in tandem with the learner's interest in following along with the song to promote learning the language. If one is clever, they could put the same lyrics into the karaoke variant of the song and practice singing to improve their reading and speaking abilities. Regardless of the reason, they user would need to find the full lyrics from the song. We want to help with this cause.

\Figure[caption="Rocket Player Displaying Song Lyrics]{res/rocket-player.png}

@@

Despite all efforts to keep our encodings straight, nothing could get Windows' command prompt, cmd, to behave as we would have wanted it to. As shown in Figure~\ref{fig:res/cmd_search_fail.png}, trying to look for the words 聞こえる and 愛 fail to produce results. We wonder if it is because the words we pass to the Java program through cmd are getting re-encoded and thereby messing up our results.

\Figure[caption="cmd.exe on Windows Failure"]{res/cmd_search_fail.png}

While testing our project, we had access to Linux computers through SSH thanks to the University of Illinois at Urbana Champaign's Engineering WorkStations (UIUC's EWS). By using the Windows program called PuTTY to interact with the Java-based searching program, we got to see perfect results as shown in Figure~\ref{fig:res/putty_search_success.png}. It raises the question of where the encoding transformations could be going wrong since PuTTY appears to be a terminal application just like cmd.

\Figure[caption="PuTTY on Windows Success"]{res/putty_search_success.png}

If we could output the search results to a web page, the encodings would be the problem of the web browser instead of the terminal. Because popular web browsers are intended to be used by people worldwide, they tend to support many text encoding formats, so there is may be better results by having a web browser interact with the Java program. We did not have the time to work on the web browser implementation though.

@@

Word distance

Comparison with Google Custom Search / Selective removal of text

Searching with many/few kanji
